\documentclass[a4paper,12pt]{article}
\usepackage{syntax}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{pgfplots}
\usepackage{listings}
\usepackage[nottoc]{tocbibind}
\setlength{\parindent}{4em} 
\usepackage{graphicx}
\graphicspath{ {images/} }
%paragraph spacing
\setlength{\parskip}{1em}

%Line spacing
\renewcommand{\baselinestretch}{1.5}
\title{A2}
\author{Kevin R. Clemmons}
\date{October 2015}

\begin{document}

\maketitle
\newpage 
%
\section{Introduction} 
I am absolutely embarrassed of this submission. By the time I got around to starting to do the carbon dating and graphs, I been battling a cold and I ran out of time.

\section{Twitter Links}
Retrieval of links from twitter was acquired through a script which produces a live stream of twitter data in json format on the console. To store the data the script extract_twitter_links.py, is run stream is piped into the file. \\ 
Processing of the json file is done in the script linkExtractor.py the content displayed in the actual text area of the tweet is stored via a key known as text. All tweets which have this are filtered through. \\ \\ 
A regular expression is then used get figure out if a link has an html link. The techniques in doing this came from the website: \begin{itemize}
    \item \verb http://adilmoujahid.com/posts/2014/07/twitter-analytics/
\end{itemize}  
Once all links have been extracted, they are then processed to determine their redirected links and whether or not the redirected links have been encountered before. If a redirected link has been encountered, it is simply ignored. \\
This process has helped me achieve a collection of 1000 links. \\
Afterwards, timemaps are retrieved and downloaded using the memento-proxy as descrbed in the assignment description. The name of each time-map is stored in a dictionary which maps the links to their time-map file name. Processing of the time map was performed using a class which was posted in the discussion board via the following link: 
\begin{itemize}
    \item \verb https://gist.github.com/jocII/c3f4a09b28fc8d590ce8
\end{itemize} 



\end{document}
