\documentclass[12pt,letterpaper]{article}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage{listings}
\usepackage{color}
\usepackage{MnSymbol,wasysym}
\usepackage{caption}
\usepackage{longtable}
\usepackage{subcaption}
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\usepackage{biblatex}

\addbibresource{bibliography.bib}

\lstdefinestyle{mystyle}{
  language=R,
  backgroundcolor=\color{backcolour},   commentstyle=\color{codegreen},
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=left,
  numbersep=5pt,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true
  tabsize=2
}

\lstset{style=mystyle}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage[margin=3cm]{geometry}
\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.05in}

% Edit these as appropriate
\newcommand\course{CS432}
\newcommand\semester{Spring 2016}     
\newcommand\hwnum{10}
\newcommand\yourname{Kevin R. Clemmons}
\newcommand\login{oduprogrammer16}

\newenvironment{answer}[1]{
  \subsubsection*{Problem #1}
}
\newenvironment{additionalsection}[1]{
    \subsection*{Last Comments}
}

\pagestyle{fancyplain}
\headheight 40pt
\lhead{\yourname\ \\(\login)\\\course\ --- \semester}
\chead{\textbf{\Large Assignment \hwnum}}
\rhead{\today}
\headsep 40pt

\begin{document}

All files mentioned in this file are uploaded into the {\it github} repository.

The \LaTeX code invovled in the generation of this document was aided by the example code provided in the links that Dr. Nelson sent out on January 17, 2016\cite{mohammedaturban2013}. \\\\

This document was compiled on \url{www.sharelatex.com} \\ \\ 

\newpage 

\begin{answer}{1}
To use the compute the nearest neighbors for \url{http://f-measure.blogspot.com/} and \url{http://ws-dl.blogspot.com/}, a program called q1.py, computes the nearest neighbor. This code was generously donated by Sandy Wilson. Tables 1 and 2 show the computations for the nearest neighbors for \url{http://f-measure.blogspot.com/} and \url{http://ws-dl.blogspot.com/}. The blog term matrix was obtained from my githum account via the following url: \url{https://github.com/oduprogrammer16/cs532-s16/blob/master/A8/src/producedFiles/blogtermmatrix.txt}

\begin{table}[ht!]
    \centering
    \begin{tabular}{|c|c|}\hline
    \textbf{K} & \textbf{Result from knnestimate()} \\\hline 
    1 & 7.0 \\\hline 
    2 & 14.0 \\\hline 
    5 & 30.0 \\\hline 
    10 & 41.7 \\\hline 
    20 & 47.95 \\\hline
    \end{tabular}
    \caption{knnestimate for \url{http://f-measure.blogspot.com/} }
    \label{tab:my_label}
\end{table}
\begin{table}[ht!]
    \centering
    \begin{tabular}{|c|c|}\hline
    \textbf{K} & \textbf{Result from knnestimate()} \\\hline 
    1 & 90.0 \\\hline 
    2 & 59.5 \\\hline 
    5 & 33.2 \\\hline 
    10 & 42.3 \\\hline 
    20 & 48.90 \\\hline
    \end{tabular}
    \caption{knnestimate for \url{http://ws-dl.blogspot.com/} }
    \label{tab:my_label}
\end{table}
\end{answer}
\newpage

\begin{answer}{2}
Unfortunately, I ran out of time to do question 2. 
\end{answer}

\newpage 
\subsection*{Additional Comments}
Had it not been for exams, this submission might have been a bit better. With that being said, I thoroughly enjoyed this class. I know I was not the best student but I definitely learned a lot. My view of the world-wide-web has radically changed. My python skill are sharper than ever before. I wish you the very best in your research. (Note: This is no attempt to try to get a better grade on this submission, it's just simple honest feedback). Lastly, my grandfather was a launchpad technician for North American Aviation. He worked in the Apollo program and was one of the launch that tried to rescue the crew during the Apollo-1 File. See this link for his testimony to what happened \url{http://as204.blogspot.com/2009/09/real-heroes-by-stephen-clemmons.html}, additional proof \url{http://www.starnewsonline.com/article/20140605/ARTICLES/140609806}
\printbibliography


\end{document}
